Capital Budget Funding in Toronto

### 2024-09-26 paper/paper.qmd
updated quarto to include scatter plots for median income and low income measure

Wards with a **\*\*** indicate a **Household Median Income** of \$84,000 or less.

@@

@@

INSERT FIGURE 2 HERE

>>>>

Rows in **red** indicate a **Household Median Income** of \$84,000 or less.

@@

```{r Figure 1, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fid-householdincome

# Scatter plot of Per Capita Funding vs Median Household Income with ward 13 removed

filtered_data <- merged_data |>
  filter(`Ward Number` != 13)

ggplot(filtered_data, aes(x = as.numeric(`Median total income of households in 2020 ($)`), y = per_capita_funding)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Per Capita Funding vs Median Household Income",
    x = "Median Household Income ($)",
    y = "Per Capita Funding ($)"
  ) +
  scale_x_continuous(labels = dollar_format()) +
  scale_y_continuous(labels = dollar_format()) +
  theme_minimal()
```

@@

INSERT FIGURE 2 HERE
```{r Figure 2, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fid-lowincome

# Scatter plot of Per Capita Funding vs Median Household Income with ward 13 removed

filtered_data <- merged_data |>
  filter(`Ward Number` != 13)

ggplot(filtered_data, aes(x = as.numeric(`Prevalence of low income based on the Low-income measure, after tax (LIM-AT) (%)`), y = per_capita_funding)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Per Capita Funding vs Prevalence of low income",
    x = "Prevalence of low income (%)",
    y = "Per Capita Funding ($)"
  ) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = dollar_format()) +
  theme_minimal()
```
```
